|

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.Rmd
revise caption

@@

```{r}
poly_conv_sim %>%
  filter(x_dist == "uniform", shape %in% c(3, 4)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(shape, log_effect_size, (RESET3_p_value:RESET9_p_value)) %>%
  pivot_longer(RESET3_p_value:RESET9_p_value) %>%
  mutate(name = gsub("_p_value", " ", name)) %>%
  mutate(name = gsub("RESET", "", name)) %>%
  mutate(name = gsub("test", "", name)) %>%
  mutate(reject = as.numeric(value < 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = name), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rev(rcartocolor::carto_pal(7, "RedOr"))) +
  theme_light() +
  labs(col = "RESET test order") +
  facet_wrap(~shape)
```

```{r}
heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Conventional test")
```

```{r}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  labs(col = "Heteroskedasticity shape") +
  ggtitle("Visual test")
```

@@

## Effect of the fitted value distribution

@@

Although the distribution of the regressor is classically not restricted by the assumptions of linear regression, it will have an impact on the visual effect of the residual plot. In our experiments, four distributions of the regressor are used to accommodate this variation.

@@

>>>>

Title 
(jokes: finding the pattern in residual tests) 
(why using visulization is important in regression diagnostics? an explanation using visual inference)
(a picture is worth a thousand word)
(a plot is worth a thousand test: )

@@

@@

## Effect of other factors

### Fitted value distribution

@@

Although the distribution of the regressor is classically not restricted by the assumptions of linear regression, it will have an impact on the distribution of the fitted values and the visual effect of the residual plot. In our experiments, four distributions of the regressor are used to accommodate this variation.

@@

### Shape

```{r eval = FALSE}
poly_conv_sim %>%
  filter(x_dist == "uniform", shape %in% c(3, 4)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(shape, log_effect_size, (RESET3_p_value:RESET9_p_value)) %>%
  pivot_longer(RESET3_p_value:RESET9_p_value) %>%
  mutate(name = gsub("_p_value", " ", name)) %>%
  mutate(name = gsub("RESET", "", name)) %>%
  mutate(name = gsub("test", "", name)) %>%
  mutate(reject = as.numeric(value < 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = name), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rev(rcartocolor::carto_pal(7, "RedOr"))) +
  theme_light() +
  labs(col = "RESET test order") +
  facet_wrap(~shape)
```

```{r poly-power-j, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model with four different shapes controlled by the parameter $j$."}

poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_type = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_type = "Visual")) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(shape)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Vivid")) +
  theme_light() +
  facet_wrap(~conv_type) +
  labs(col = "Non-linearity shape")
```

```{r heter-power-a, fig.cap = "Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$."}

heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  mutate(conv_type = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  mutate(conv_type = "Visual")) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  facet_wrap(~conv_type) +
  labs(col = "Heteroskedasticity shape")
```
